Users Guide for Corrfunc

### 2016-02-02 paper/users-guide.tex
Added some protection for C++ compilers. Switched the objects files to the front for the Makefiles
Updated the logic in DDrppi to remove using the comoving distance array. Now, I check for max. separation before proceeding with the division

%% Some of the short-cuts I use
\newcommand{\rmax}{\ensuremath{{r_{max}}}\xspace}
\newcommand{\xir}{\ensuremath{{\xi(r)}}\xspace}
\newcommand{\wprp}{\ensuremath{{w_p(r_p)}}\xspace}
\newcommand{\xirppi}{\ensuremath{{\xi(r_p,\pi)}}\xspace}
\newcommand{\pimax}{\ensuremath{{\pi_{\rm max}}}\xspace}
\newcommand{\hMpc}{\ensuremath{{h^{-1}Mpc}}\xspace}
\newcommand{\todo}[1]{\marginpar{TODO}{\color{red}#1}}
\newcommand{\clang}{{\texttt{clang}}\xspace}
\newcommand{\icc}{{\texttt{icc}}\xspace}
\newcommand{\gcc}{{\texttt{gcc}}\xspace}

@@

\subsection{Getting the Source}
You can obtain the source in two ways: i) Clone the mercurial repo (\texttt{hg clone} \url{https://bitbucket.org/manodeep/corrfunc/}) 
or ii) Download the tar archive (\href{https://bitbucket.org/manodeep/corrfunc/downloads/corrfunc.1.0.0.tar.gz}{corrfunc.\$MAJOR.0.\$MINOR.tar.gz}) and 
unpack it in the directory where you wish to keep the files (\texttt{tar xvzf}\\ \texttt{corrfunc.\$MAJOR.0.\$MINOR.tar.gz}). Here, \texttt{\$MAJOR}
and \texttt{\$MINOR} refer to the major and minor release versions (current \texttt{\$MAJOR=1}, \texttt{\$MINOR=0}). I will only change 
the \texttt{\$MAJOR} version in the highly unlikely event that the API changes.

\subsection{Directory Structure}
The directory structure for the code looks like this:
\dirtree{%
.1 corrfunc.
.2 paper.
.2 io\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for reading in data{.} 
  \end{minipage}.
.2 utils\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for creating grids and helper routines{.} 
  \end{minipage}.
.2 bin\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy executable files when you run `make install'{.} 
  \end{minipage}.
.2 include\DotFill 
  \begin{minipage}[t]{8cm}
    Header files for static libraries{.} 
  \end{minipage}.
.2 lib\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy static libraries and python library after you run `make'{.} 
  \end{minipage}.
.2 xi\_theory.
.3 benchmarks\DotFill
  \begin{minipage}[t]{8cm}
    IDL scripts to run benchmarks{.} 
  \end{minipage}.
.3 examples\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for example C bindings using the static libraries{.} 
  \end{minipage}.
.3 python\_bindings\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to generate python bindings{.} 
  \end{minipage}.
.3 tests\DotFill 
  \begin{minipage}[t]{8cm}
    Correct outputs for tests{.}
  \end{minipage}.
.4 data\DotFill 
  \begin{minipage}[t]{8cm}
    Mock galaxy catalogs for tests{.} 
  \end{minipage}.
.3 xi\_of\_r\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\xi(r)${.} 
  \end{minipage}.
.3 xi\_rp\_pi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r_p,\pi)${.} 
  \end{minipage}.
.3 wp\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $w_p(r_p)${.} 
  \end{minipage}.
.3 xi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r)$ directly on a periodic cube{.} 
  \end{minipage}.
.3 vpf\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to compute the counts-in-spheres statistic{.} 
  \end{minipage}.

.2 xi\_mocks.
.3 benchmarks\DotFill
  \begin{minipage}[t]{8cm}
    IDL scripts to run benchmarks for mocks{.} 
  \end{minipage}.
.3 examples\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for example C bindings using the static libraries for mocks{.} 
  \end{minipage}.
.3 python\_bindings\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to generate python bindings for mocks{.} 
  \end{minipage}.
.3 tests\DotFill 
  \begin{minipage}[t]{8cm}
    Correct outputs for tests for mocks{.}
  \end{minipage}.
.4 data\DotFill 
  \begin{minipage}[t]{8cm}
    Mock galaxy catalogs for tests on a sphere{.} 
  \end{minipage}.
.3 DDrppi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\xi(r_p,\pi)$ on mocks{.} 
  \end{minipage}.
.3 wtheta\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\omega(\theta)$ {.} 
  \end{minipage}.
.3 vpf\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to compute the counts-in-spheres statistic on mocks{.} 
  \end{minipage}.
}

@@

\begin{table}
\centering
\caption{\footnotesize OpenMP scaling for the three codes. Efficiencies are defined 
as \texttt{Speedup/Nthreads}. Note, that \xir has super-linear scaling with \texttt{nthreads}
up to $\sim$ 8 threads.}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{cccc} 
\toprule
\multirow{2}{*}{\textbf{Nthreads}}   &
\multicolumn{3}{c}{\textbf{Efficiency[\%]}} \\
\cmidrule(l{1.0em}r{1.0em}){2-4}
&
\multicolumn{1}{c}{$\boldsymbol{\xir}$}   &
\multicolumn{1}{c}{$\boldsymbol{\xirppi}$} &
\multicolumn{1}{c}{$\boldsymbol{\wprp}$}     \\
\midrule
\input{timings_Mr19_openmp} 
\bottomrule
\end{tabular}
\end{adjustbox}
\label{table:openmp}
\end{table}

>>>>

%% Some of the short-cuts I use
\newcommand{\rmax}{\ensuremath{{r_{max}}}\xspace}
\newcommand{\xir}{\ensuremath{{DD(r)}}\xspace}
\newcommand{\xiofr}{\ensuremath{{\xi(r)}}\xspace}
\newcommand{\wprp}{\ensuremath{{w_p(r_p)}}\xspace}
\newcommand{\xirppi}{\ensuremath{{\xi(r_p,\pi)}}\xspace}
\newcommand{\pimax}{\ensuremath{{\pi_{\rm max}}}\xspace}
\newcommand{\hMpc}{\ensuremath{{h^{-1}Mpc}}\xspace}
\newcommand{\todo}[1]{\marginpar{TODO}{\color{red}#1}}
\newcommand{\clang}{{\texttt{clang}}\xspace}
\newcommand{\icc}{{\texttt{icc}}\xspace}
\newcommand{\gcc}{{\texttt{gcc}}\xspace}

@@

\subsection{Getting the Source}
You can obtain the source in two ways: i) Clone the git repo (\texttt{git clone} \url{https://github/manodeep/Corrfunc/}) 
or ii) Download the tar archive (\href{https://github.com/manodeep/Corrfunc/releases/latest}{Corrfunc.\$MAJOR.\$MINOR.\$PATCH.tar.gz}) and 
unpack it in the directory where you wish to keep the files (\texttt{tar
  xvzf}\\ \texttt{Corrfunc.\$MAJOR.\$MINOR.\$PATCH.tar.gz}). Here,
\texttt{\$MAJOR}, \texttt{\$MINOR} and \texttt{\$PATCH} refer to the major,
minor and patch release versions (current \texttt{\$MAJOR=0},
\texttt{\$MINOR=2}, \texttt{\$PATCH=0}). I will only change 
the \texttt{\$MAJOR} version in the highly unlikely event that the API changes.

\subsection{Directory Structure}
The directory structure for the code looks like this:
\dirtree{%
.1 corrfunc.
.2 paper.
.2 io\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for reading in data{.} 
  \end{minipage}.
.2 utils\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for creating grids and helper routines{.} 
  \end{minipage}.
.2 bin\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy executable files when you run `make install'{.} 
  \end{minipage}.
.2 include\DotFill 
  \begin{minipage}[t]{8cm}
    Header files for static libraries{.} 
  \end{minipage}.
.2 lib\DotFill 
  \begin{minipage}[t]{8cm}
    Will be created to copy static libraries and python library after you run `make'{.} 
  \end{minipage}.
.2 xi\_theory.
.3 benchmarks\DotFill
  \begin{minipage}[t]{8cm}
    IDL scripts to run benchmarks{.} 
  \end{minipage}.
.3 examples\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for example C bindings using the static libraries{.} 
  \end{minipage}.
.3 python\_bindings\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to generate python bindings{.} 
  \end{minipage}.
.3 tests\DotFill 
  \begin{minipage}[t]{8cm}
    Correct outputs for tests{.}
  \end{minipage}.
.4 data\DotFill 
  \begin{minipage}[t]{8cm}
    Mock galaxy catalogs for tests{.} 
  \end{minipage}.
.3 xi\_of\_r\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\xi(r)${.} 
  \end{minipage}.
.3 xi\_rp\_pi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r_p,\pi)${.} 
  \end{minipage}.
.3 wp\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $w_p(r_p)${.} 
  \end{minipage}.
.3 xi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for $\xi(r)$ directly on a periodic cube{.} 
  \end{minipage}.
.3 vpf\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to compute the counts-in-spheres statistic{.} 
  \end{minipage}.
.2 xi\_mocks.
.3 benchmarks\DotFill
  \begin{minipage}[t]{8cm}
    IDL scripts to run benchmarks for mocks{.} 
  \end{minipage}.
.3 examples\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for example C bindings using the static libraries for mocks{.} 
  \end{minipage}.
.3 python\_bindings\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to generate python bindings for mocks{.} 
  \end{minipage}.
.3 tests\DotFill 
  \begin{minipage}[t]{8cm}
    Correct outputs for tests for mocks{.}
  \end{minipage}.
.4 data\DotFill 
  \begin{minipage}[t]{8cm}
    Mock galaxy catalogs for tests on a sphere{.} 
  \end{minipage}.
.3 DDrppi\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\xi(r_p,\pi)$ on mocks{.} 
  \end{minipage}.
.3 wtheta\DotFill 
  \begin{minipage}[t]{8cm}
    Source files for getting pair-counts to compute $\omega(\theta)$ {.} 
  \end{minipage}.
.3 vpf\DotFill 
  \begin{minipage}[t]{8cm}
    Source files to compute the counts-in-spheres statistic on mocks{.} 
  \end{minipage}.
}

@@

\begin{table}
\centering
\caption{\footnotesize OpenMP scaling for the three codes. Efficiencies are defined 
as \texttt{Speedup/Nthreads}. Note, that \xir has super-linear scaling with \texttt{nthreads}
up to $\sim$ 10 threads.}
\begin{adjustbox}{max width=\textwidth}
\begin{tabular}{ccccccccc} 
\toprule
\multirow{3}{*}{\textbf{Nthreads}}   &
\multicolumn{8}{c}{\textbf{Efficiency[\%]}} \\
\cmidrule(l{3em}r{3em}){2-9}

                                     &
\multicolumn{4}{c}{\textbf{Periodic Boxes}}  &
\multicolumn{4}{c}{\textbf{Spherical Geometry}}  \\
\cmidrule(l{1.0em}r{1.0em}){2-5}
\cmidrule(l{1.0em}r{1.0em}){6-9}
                                               &
\multicolumn{1}{c}{$\boldsymbol{\xir}$}        &
\multicolumn{1}{c}{$\boldsymbol{\xirppi}$}     &
\multicolumn{1}{c}{$\boldsymbol{\wprp}$}       & 
\multicolumn{1}{c}{$\boldsymbol{\xiofr}$}      &
\multicolumn{1}{c}{$\boldsymbol{DD(r_p,\pi)}$} &
\multicolumn{1}{c}{$\boldsymbol{DD(\theta)}$}  &
\multicolumn{1}{c}{$\boldsymbol{DR(r_p,\pi)}$} & 
\multicolumn{1}{c}{$\boldsymbol{DR(\theta)}$}   \\
\midrule
\input{timings_Mr19_openmp_theory_and_mocks}
\bottomrule
\end{tabular}
\end{adjustbox}
\label{table:openmp}
\end{table}
